---
title: "Info about R packages and Python modules"
author: "Ana Martinovici"
date: "Last compiled on `r Sys.Date()`"
output: 
    html_document:
        css: style.css
        toc: true
        toc_float: 
            collapsed: false
        number_sections: true
        code_folding: hide
        theme: cerulean
editor_options: 
  chunk_output_type: console
---

# R version 

```{r}
R.version
```

# R session info

```{r}
sessionInfo()
```

# Versions of R packages

```{r}

packages_used <- c("bayesplot",
				   "bayestestR",
				   "brms",
				   "dplyr",
				   "eegUtils",
				   "emmeans",
				   "ggplot2",
				   "here",
				   "patchwork",
				   "remotes",
				   "reticulate",
				   "rmarkdown",
				   "Rmisc",
				   "tidybayes",
				   "tidyverse",
				   "tools",
				   "viridis")

print_pkg_details <- function(pkg_name) {
	paste0(pkg_name, ": ", packageVersion(pkg_name))
}
	
sapply(packages_used, print_pkg_details, simplify = TRUE, USE.NAMES = FALSE)
```

# R packages citations

```{r}

sapply(packages_used, citation)

```

# Python version - reticulate config

```{r}
reticulate::py_discover_config()

```

# Versions of Python modules

Note that `__version__` is not set for the standard library modules such as `os`. Modules in the standard library do not have individual versions but follow the Python version.

```{python}

import autoreject
print("autoreject version: " + autoreject.__version__)

#import glob
#print("glob version: " + glob.__version__)

import mne
print("mne version: " + mne.__version__)

import mne_bids
print("mne_bids version: " + mne_bids.__version__)

import numpy
print("numpy version: " + numpy.__version__)

#import os
#print("os version: " + os.__version__)

import pandas
print("pandas version: " + pandas.__version__)

#import pathlib
#print("pathlib version: " + pathlib.__version__)

import pyprep
print("pyprep version: " + pyprep.__version__)

#import random
#print("random version: " + random.__version__)

#import sys
#print("sys version: " + sys.__version__)

#import time
#print("time version: " + time.__version__)


```


# RStudio

RStudio 2022.02.2+485 "Prairie Trillium" Release (8acbd38b0d4ca3c86c570cf4112a8180c48cc6fb, 2022-04-19) for Windows

Mozilla/5.0 (Windows NT 10.0; Win64; x64) AppleWebKit/537.36 (KHTML, like Gecko) QtWebEngine/5.12.8 Chrome/69.0.3497.128 Safari/537.36